Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2024-09-18 whittaker.tex
More proofreading

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand{\gder}{\mathfrak g_{\mathrm{der}}}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\KS}{\mathcal{KS}}
\newcommand{\Wh}{\mathrm{Wh}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
\begin{document}
\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams \& Alexandre Afgoustidis}
\maketitle

@@

Recall that a representation $\pi$ of~$G(\R)$ is said to {have a $(B,\eta)$-Whittaker model} if it has a nonzero distribution vector on which $N(\R)$ acts by $\eta$ (for a more careful statement of the definition see Section~\ref{sec:invariants}).
This condition only depends on the conjugacy class of the pair, 
so we  consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class as a 
as a {\it Whittaker datum}.
If $\w$ is a Whittaker datum, it makes sense to talk about $\pi$ having a $\w$-Whittaker model. We let $\Wh(\pi)$  be the set of
Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model. This is a small finite set.
We say $\pi$ is {\it generic} if $\Wh(\pi)$ is non-empty.

The set $\Wh(\pi)$ is
a useful invariant of generic representations.
For instance if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum, then $\Pi$ contains a unique representation $\pi$
having a $\w$-Whittaker model. This plays a role in describing the internal structure of $L$-packets.
If $\Pi$ is a discrete series $L$-packet then each generic representation in the packet has a unique
Whittaker model, so the generic representations in $\Pi$ are parametrized by their Whittaker models.
It is conjectured that these properties hold in the $p$-adic case as well, and this is known in many cases.

There are other invariants attached to an
irreducible representation $\pi$.  We will be concerned with two of
them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$
which is an analytic invariant.
The second is the \emph{associated variety} $\AV(\pi)$, which is
defined  algebraically.
Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as
coadjoint orbits (of two different kinds).
The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.

@@

Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$.
Let $\g=\Lie(G), \g(\R)=\Lie(G(\R))$. 
Choose a Cartan involution $\theta$ for $G$. This means:
$\theta$ is an algebraic involution, commuting with~$\sigma$,
and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$, $K(\R)=G(\R)^\theta=K^\sigma$.
Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$
(we use the same notation for $\sigma,\theta$ lifted to $\g$).

\subsubsection*{Nilpotent orbits in $\g^*$} 
\label{s:dual}
Let $\N$ be the set of nilpotent elements of $\g$.

We need to pass to the dual Lie algebra $\g^*$, and it is important to do this as canonically as possible, i.e. independent of a choice
of isomorphism $\g\simeq\g^*$. First we define the nilpotent cone in $\g^*$ as follows. 
We say an element of $\g^*$ is nilpotent if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by $\C^*$,
and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.
Let $\N^*$ be the set of nilpotent elements.
The principal nilpotent orbit $\O_p\in \N^*$ is the set of regular nilpotent elements, and $\overline{\O_p}=\N^*$.

The statements of the main results do not require the choice of an isomorphism $\g\simeq \g^*$. However such a choice appears in the proofs so we spell this out.
Having a $G(\R)$-invariant bilinear form on $\g(\R)$ is equivalent to having a $G(\R)$-equivariant isomorphism $\g(\R)\simeq \g^*(\R)$. 
Suppose we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate, $G(\C)$ and Galois invariant
bilinear form on $\g$. The restriction of the form each simple factor
is unique up to a non-zero constant. For example we can use the Killing form on $\gder$, extended arbitrarily by a non-degenerate form on the center.

Given $\kappa$ we define
$\psi_\kappa: \g\rightarrow \g^*$ as usual:
$$
\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in\g).
$$

Using $\psi_\kappa$ we transfer the asymptotic cone, Kostant section, and Kostant Sekiguchi corresondence to $\g^*$. In each case these constructions are independent of the
choice of $\kappa$. See Section \ref{sec:Sekiguchi}.
In Section \ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)

@@

A related invariant is the associated variety of the annihilator $I_\pi$ of $\pi$ in the universal enveloping algebra, 
denoted $\AVann(\pi)$.
This is a subset of $\N^*\subset\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.

@@

Now suppose $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. 
The \emph{wave-front
  set} $\WF(\pi)$ is an analytic invariant determined by the
singularities of the global character of $\pi$ near the identity. See \cite{howe_wave_front, bv_local_structure, HarrisHeOlafsson} for the definition. 
The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in
$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits.

@@

Suppose again that $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. We consider the attached representations of~$\pi$ on the space $\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$. Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction. We say $\pi$ has a $(B,\eta)$-Whittaker model
if there exists a nonzero element $v$ in $\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$. See \cite{matumoto}. If~$\w$ is the corresponding Whittaker datum, i.e. the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a $\w$-Whittaker model.

@@

\begin{lemma}
  \label{l:large}
  The following conditions are equivalent.
  \begin{enumerate}
  \item $\pi$ is large;
        \item $\pi$ is generic.
\item $\AVann(\pi)=\N^*=\overline{\Op}$;
\item $\dim(\AVann(\pi))=N$;
  \item $\dim(\AV(\pi))=N/2$;
  \item $\GK(\pi)=N/2$;
\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

@@

Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$. In fact, suppose~$\lambda$ is an element of~$\Lambda$ and $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$. Every discrete series representation arises in this way, and $\pi_{\lambda, \zeta}=\pi_{\lambda', \zeta'}$ if and only if $\zeta=\zeta'$ and $\lambda, \lambda'$ are $W_K$-conjugate. See  \cite[Section 8]{AV1} and \cite{Contragredient} for more on the parametrization.

@@

\begin{proposition} \label{invariants_ds}
  Suppose $\pi$ is a generic discrete series representation of $G(\R)$. Then:
\begin{enumerate}[(a)]
\item $\Wh(\pi)$ is a single Whittaker datum;
\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \s^*$;
\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)^*$.
\end{enumerate}
\end{proposition}

@@

Because of Proposition~\ref{invariants_ds} we will abuse notation slightly, as follows. If~$\pi$ is a generic discrete series representation of~$G(\R)$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O\subset \s^*$.
Similarly we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of the $G(\R)$-orbit $\O\subset i\g(\R)^*$.

@@

\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be a~$Q$-equivariant map. 
\begin{itemize}
\item[(a)] If $Q$ acts transitively on~$B$,  then~$f$ is surjective\textup{;}
\item[(b)] If $Q$ acts transitively on~$A$ and freely on~$B$, then~$f$ is injective.
\end{itemize}
In particular, if~$Q$ acts transitively on~$A$ and simply transitively on~$B$, then~$f$ must be a bijection and the action of~$Q$ on~$A$ must be simply transitive.
\end{lemma}

@@

The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-reoresentations. If~$q$ is an element of~$Q_\sigma(G)$, we write $\pi \mapsto \pi^q$ for the action of~$q$ on equivalence classes of $G(\R)$-representations.

@@

These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q}:

\begin{lemma}\label{lem:action_q}
Suppose $\pi$ is the equivalence class of an irreducible Hilbert space representation of $G(\R)$. 
Suppose $q\in Q_\sigma(G)$. 
Then $(\pi^q)_K\simeq (\pi_K)^{\phi(g)}$.
\end{lemma}

\begin{proof}
Immediate from Lemma~\ref{lem:iso_q} and the definition of the actions.
\end{proof}

@@

\begin{proof}
The proof of~(1) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)^*$,
and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)^*$ the condition $X'\in i\g(\R)^*$ 
is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
A standard fact is that $H^1(\sigma, U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we can assume $g\inv \sigma(g)\in Z$. This is equivalent to: the image of $g$ in $\Gad$ is in $\Gad(\R)$. On the other hand $\omega=\omega'$ 
if and only if $X'=\Ad(g)X$ for some $g\in G(\R)$. This competes the proof of (1).

@@

On the other hand $Q(G)$, realized as $Q_\theta(G)$ is a group of automorphisms of $(\g,K)$.
It induces actions on $\s^*$, $\Op$ and $\Op\cap\s^*$, and on $(\g,K)$-modules.

@@

In this section only we need to  choose a particular an isomorphism $\gder\simeq \gder^*$.
For this we let $\kappa$ be the killing form, and define $\psi:\gder\rightarrow \gder^*$ by
$$
\psi(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
$$

@@

\begin{equation}
  \label{e:Fpi}
  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}\in \N.
\end{equation}

Then $F_\pi\in\s$ is a regular nilpotent element.
Then 
$$
\AV(\pi)=K\cdot \psi(F_\pi).
$$
\end{lemma}
See
\cite[Propositions A.7 and A.9]{AV1}.

@@

For this see \cite{HarrisHeOlafsson}; in the special casea considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed

@@

The following discussion is taken directly from \cite[Section~3.1]{adams_kaletha}.

Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. 
The corresponding Borel subgroup $B$ is defined over $\R$.
Choose an $\R$-Cartan subgroup $T$ of
$\overline B$, and let $B$ be the corresponding opposite Borel
subgroup (characterized by $B\cap \overline B=T$). 
Then $X$ defines a unitary
character of the nilradical  $N(\R)$  of $B(\R)$ by
\[ 
\psi_X(\exp Y)=e^{X(Y)}\quad (Y\in\n(\R)).
\] 
We define $\w_X$ to be the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$; as the notation indicates this is independent 
of the choice of $T$.

@@

We define the Kostant section in $\g^*$ using an identification $\g\simeq \g^*$ as discussed in Section \ref{s:dual}. That is we fix an equivariant isomorphism $\psi$, and define
$$
\K(X)=\psi(\K(\psi\inv(X))\quad (X\in \g^*)
$$
Since $\psi$ is unique on each simple factor up to non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.

@@

\begin{lemma}[\phantom{}{\cite[Lemma 3.3.4]{adams_kaletha}}]
\label{lem:Kost_and_AC}
Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element. Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$. 
\end{lemma}

@@

The Proposition, Lemma and Lemma \ref{lem:WF_and_AC} give the following result,
which is a special case of the main result of \cite{matumoto} (Theorem A).

@@

Write $\O_H$ for the $G(\R)$-orbit of $H$.

@@

\begin{proof}[proof of the  Proposition]
For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.

@@

The second assertion is an immediate consequence of the first and Lemma \ref{lem:Kost_and_AC}

\end{proof}

@@

\subsection{$\AV(\pi)$ and $\WF(\pi)$: the Kostant--Sekiguchi correspondence } \label{sec:Sekiguchi}

@@

It is well known that there is a natural bijection between nilpotent $G(\R)$-orbits on $\g(\R)$ and nilpotent $K$ orbits on $\s$. 
This is the Kostant--Sekiguchi
correspondence~\cite{sekiguchi}, which we write as $\KS(\O)$. It is a deep theorem of
Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront
set and the associated variety are related by this
correspondence. (As a historical aside, the Kostant--Sekiguchi
correspondence was discovered on the basis that the correspondence
$\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary
terms.)

@@

We need the corresponding result in $\g^*$. As discussed in Section \ref{s:dual} this uses a choice of an isomorphism $\g\simeq \g^*$, but the result is independent of this choice.
That is for $X\in \O_p\subset \g^*$ we have
$$
\KS(K\cdot X)=\psi_c(\KS(K\cdot \psi_c\inv(X)),
$$
independent of the choice of $\psi$.

@@

\subsection{Appendix: $SL(2,\R)$ calculation}

We illustrate these results with the illustrative example of $SL(2,\R)$,.

>>>>

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand{\gder}{\mathfrak g_{\mathrm{der}}}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\KS}{\mathrm{KS}}
\newcommand{\Wh}{\mathrm{Wh}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
\begin{document}
\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams \& Alexandre Afgoustidis}
\maketitle

@@

Recall that a representation $\pi$ of~$G(\R)$ is said to {have a $(B,\eta)$-Whittaker model} if it has a nonzero distribution vector on which $N(\R)$ acts by $\eta$ (for a more careful statement of the definition see Section~\ref{sec:invariants}).
This condition only depends on the conjugacy class of the pair, 
so we  consider pairs $(B,\eta)$ modulo conjugation by $G(\R)$, and refer to such a conjugacy class
as a {\it Whittaker datum}.
If $\w$ is a Whittaker datum, it makes sense to talk about $\pi$ having a $\w$-Whittaker model. We let $\Wh(\pi)$  be the set of
Whittaker data $\w$ such that $\pi$ has a $\w$-Whittaker model. This is a small finite set.
We say $\pi$ is {\it generic} if $\Wh(\pi)$ is non-empty.

The set $\Wh(\pi)$ is
a useful invariant of generic representations.
For instance, in the local Langlands correspondence, if $\Pi$ is a tempered $L$-packet for $G(\R)$ and $\w$ is a Whittaker datum, then $\Pi$ contains a unique representation
having a $\w$-Whittaker model. This plays a role in describing the internal structure of $L$-packets.
If $\Pi$ is a discrete series $L$-packet then each generic representation in the packet has a unique
Whittaker model, so the generic representations in $\Pi$ are parametrized by their Whittaker models.
It is conjectured that these properties hold in the $p$-adic case as well, and this is known in many cases.

There are other invariants attached to an
irreducible representation $\pi$.  We will be concerned with two of
them, defined very differently. The first is the \emph{wavefront set} $\WF(\pi)$,
which is an analytic invariant.
The second is the \emph{associated variety} $\AV(\pi)$, which is
defined  algebraically.
Both consist of nilpotent elements of the dual of the Lie algebra of~$G$, and are defined as
coadjoint orbits (of two different kinds).
The invariants $\Wh(\pi), \WF(\pi)$ and $\AV(\pi)$ are closely related to each other.

@@

Let~$\sigma$ be the anti-holomorphic involution defining~$G(\R)$.
Set $\g=\Lie(G)$ and $\g(\R)=\Lie(G(\R))$. 
Choose a Cartan involution $\theta$ for $G$. This means:
$\theta$ is an algebraic involution, commuting with~$\sigma$,
and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
Let $\s$ be the $-1$ eigenspace of $\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions.

\subsubsection*{Nilpotent orbits in $\g^*$} 
\label{s:dual}
Let $\N$ be the set of nilpotent elements of $\g$. Several of the invariants below are related to~$\N$, but are more naturally defined as subsets of the dual vector space~$\g^\ast$.
Therefore we need to pass to the dual Lie algebra $\g^*$, and it is important to do this as canonically as possible, i.e. in a manner as independent as possible of a choice
of isomorphism $\g\simeq\g^*$.

First we define the nilpotent cone in $\g^*$ as follows. 
We say an element of~$\g^*$ is \emph{nilpotent} if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by~$\C^*$,
and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.
Let $\N^*$ be the set of nilpotent elements.
The principal nilpotent orbit $\O_p\in \N^*$ is the set of regular nilpotent elements, and $\overline{\O_p}=\N^*$.

The statements of the main results below do not require the choice of an isomorphism $\g\simeq \g^*$. However such a choice appears in the proofs, so we spell this out.
Having a $G(\R)$-invariant bilinear form on $\g(\R)$ is equivalent to having a $G(\R)$-equivariant isomorphism $\g(\R)\simeq \g^*(\R)$. 
Suppose we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate bilinear form on~$\g$ which is both $G(\C)$- and Galois-invariant. The restriction of the form to each simple factor
is unique up to a nonzero constant. For example we can use the Killing form on $\gder=[\g, \g]$, extended arbitrarily by a non-degenerate form on the center.

Given such a non-degenerate bilinear form $\kappa$, we define
$\psi_\kappa: \g\rightarrow \g^*$ as usual:
$$
\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in\g).
$$

Using $\psi_\kappa$ we shall transfer to $\g^\ast$ several notions usually defined on $\g$: the asymptotic cone, the Kostant section, and the Kostant--Sekiguchi corresondence. In each case the resulting notions are independent of the
choice of $\kappa$. See Section~\ref{sec:Sekiguchi}.
In Section~\ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)

@@

A related invariant is the associated variety of the annihilator $I_\pi$ of $\pi$ in the universal enveloping algebra, 
denoted $\AVann(\pi)$.
This is a subset of $\N^*\subset\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}. Both $\AV(\pi)$ and $\AVann(\pi)$ depend only on the equivalence class of~$\pi$.

@@

Now suppose $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. 
The \emph{wave-front
  set} $\WF(\pi)$ is an analytic invariant determined by the
singularities of the global character of $\pi$ near the identity. See \cite{howe_wave_front, bv_local_structure, HarrisHeOlafsson} for the definition. 
The set~$\WF(\pi)$  is a closed $G(\R)$-invariant subset of the nilpotent cone in
$i\g(\R)^*$. As such it is the union of a finite number of nilpotent $G(\R)$-orbits. Again, this depends only on the equivalence class of~$\pi$.

@@

Suppose again that $\pi$ is an irreducible admissible representation of $G(\R)$ on a Hilbert space $\mH$. We consider the corresponding actions of $G(\R)$ on the space~$\mH^\infty$ of smooth vectors in $\mH$, and on its dual $\mH^{-\infty}$; and we still denote them by~$\pi$. Let~$(B, \eta)$ be a pair satisfying conditions (i)-(ii) of the Introduction. We say $\pi$ has a $(B,\eta)$-Whittaker model
if there exists a nonzero element $v$ in~$\mH^{-\infty}$ such that $\pi(n)(v)=\eta(n)v$ for all $n$ in the nilradical $N(\R)$ of $B(\R)$. See~\cite{matumoto}. If~$\w$ is the corresponding Whittaker datum, i.e. the $G(\R)$-conjugacy class of the pair $(B, \eta)$, we say~$\pi$ has a $\w$-Whittaker model.

@@

\begin{lemma}
  \label{l:large}
  The following conditions are equivalent.
  \begin{enumerate}
  \item $\pi$ is large\textup{;}
        \item $\pi$ is generic\textup{;}
\item $\AVann(\pi)=\N^*=\overline{\Op}$\textup{;}
\item $\dim(\AVann(\pi))=N$\textup{;}
  \item $\dim(\AV(\pi))=N/2$\textup{;}
  \item $\GK(\pi)=N/2$.
\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

@@

Then any discrete series representation of~$G(\R)$ has a \emph{Harish-Chandra parameter}, which is an element of~$\Lambda/W_K$. In fact, suppose~$\lambda$ is an element of~$\Lambda$ and suppose $\zeta$ is a character of the center~$Z(\R)$ of~$G(\R)$ whose differential agrees with~$\lambda-\rho$ on the intersection $T(\R) \cap Z(\R)$; then the pair $(\lambda, \zeta)$  determines a discrete series representation~$\pi_{\lambda, \zeta}$ of~$G(\R)$. Every discrete series representation arises in this way, and $\pi_{\lambda, \zeta}=\pi_{\lambda', \zeta'}$ if and only if $\zeta=\zeta'$ and $\lambda, \lambda'$ are $W_K$-conjugate. See  \cite[Section 8]{AV1} and \cite{Contragredient} for more on the parametrization.

@@

\begin{proposition} \label{invariants_ds}
  Suppose $\pi$ is a generic discrete series representation of $G(\R)$. Then\textup{:}
\begin{enumerate}[(a)]
\item $\Wh(\pi)$ is a single Whittaker datum\textup{;}
\item $\AV(\pi)$ is the closure of a single $K$-orbit on~$\mathcal{O}_p \cap \s^*$\textup{;}
\item  $\WF(\pi)$ is the closure of a single $G(\R)$-orbit on $\mathcal{O}_p \cap  i \g(\R)^*$\textup{.}
\end{enumerate}
\end{proposition}

@@

Because of Proposition~\ref{invariants_ds} we will abuse notation slightly, as follows. If~$\pi$ is a generic discrete series representation of~$G(\R)$ and~$\O$ is a $K$-orbit in~$\s^\ast$, we write $AV(\pi)=\O$ to indicate that $AV(\pi)$ is the closure of the $K$-orbit $\O$. 
Similarly, if $\O\subset i\g(\R)^*$ is a $G(\R)$-orbit, we write $\WF(\pi)=\O$ to indicate that $\WF(\pi)$ is the closure of~$\O$.

@@

\begin{lemma} Suppose a group $Q$ acts on two sets $A, B$ and let $f\colon A \to B$ be a $Q$-equivariant map. 
\begin{itemize}
\item[(a)] If $Q$ acts transitively on~$B$,  then~$f$ is surjective\textup{;}
\item[(b)] If $Q$ acts transitively on~$A$ and freely on~$B$, then~$f$ is injective.
\end{itemize}
In particular, if~$Q$ acts transitively on~$A$ and simply transitively on~$B$, then~$f$ must be a bijection and the action of~$Q$ on~$A$ must be simply transitive.
\end{lemma}

@@

The adjoint action of $\Gad^\sigma$ on~$G(\R)$ induces an action on $G(\R)$-representations, which descends to an action of  $Q_\sigma(G)$ on equivalence class of $G(\R)$-representations. If~$q$ is an element of~$Q_\sigma(G)$, we write $\pi \mapsto \pi^q$ for the action of~$q$ on equivalence classes of $G(\R)$-representations.

@@

These two actions are intertwined by the isomorphism of Lemma~\ref{lem:iso_q} (this follows immediately from the definitions of the actions and of that isomorphism):

\begin{lemma}\label{lem:action_q}
Suppose $\pi$ is the equivalence class of an irreducible Hilbert space representation of $G(\R)$. 
Suppose $q\in Q_\sigma(G)$. 
Then $(\pi^q)_K\simeq (\pi_K)^{\varphi(g)}$.
\end{lemma}

@@

\begin{proof}
The proof of~(1) is a standard argument in group cohomology. Suppose $\omega,\omega'$ are $G(\R)$ orbits in $\Op\cap i\g(\R)^*$,
and choose $X\in \omega,X'\in\omega'$. Then there exists $g\in G$ such that $\Ad(g)(X)=X'$. Since $X\in \g(\R)^*$ the condition $X'\in i\g(\R)^*$ 
is $g\inv \sigma(g)\in \Stab_G(X)$.  Since $X$ is principal, we have $\Stab_G(X)=ZU$ where $U$ is a unipotent group. 
A standard fact is that $H^1(\sigma, U)=1$ \cite[Chap.~III, Proposition~6]{Serre_Galois}, and from this we see that, after multiplying $g$ on the right by an element of $u$, we may assume $g\inv \sigma(g)\in Z$. This is equivalent to: the image of $g$ in $\Gad$ is in $\Gad(\R)$. On the other hand $\omega=\omega'$ 
if and only if $X'=\Ad(g)X$ for some $g\in G(\R)$. This competes the proof of (1).

@@

On the other hand $Q(G)$, realized as $Q_\theta(G)$, is a group of automorphisms of $(\g,K)$.
It induces actions on $\s^*$, $\Op$ and $\Op\cap\s^*$, and on $(\g,K)$-modules.

@@

In this section only we need to  choose a particular an isomorphism $\gder\simeq \gder^*$.
For this we let $\kappa$ be the killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
$$
\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
$$

@@

\begin{equation}
  \label{e:Fpi}
  F_\pi=\sum_{\alpha\in S(\lambda)}X_{-\alpha}
\end{equation}
Then $F_\pi\in\s$ is a regular nilpotent element, belongs to~$\gder$, and satisfies: 
$$
\AV(\pi)=K\cdot \psi_\kappa(F_\pi).
$$
\end{lemma}
See
\cite[Propositions A.7 and A.9]{AV1}.

@@

For this see \cite{HarrisHeOlafsson}; in the special case considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed

@@

The following discussion summarizes results from \cite[Section~3]{adams_kaletha}.

Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. This is the Lie algebra of~$\overline{B}(\R)$, where$\overline{B}$ is a Borel subgroup of~$G$ defined over $\R$.
Choose an $\R$-Cartan subgroup $T$ of
$\overline B$, and let~$B$ be the  Borel
subgroup opposite to~$\overline{B}$, characterized by $B\cap \overline B=T$.
Then $X$ defines a unitary
character of the nilradical  $N(\R)$  of $B(\R)$ by
\[ 
\psi_X(\exp Y)=e^{X(Y)}\quad (Y\in\n(\R)).
\] 
We define $\w_X$ to be the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$; as the notation indicates this is independent 
of the choice of $T$.

@@

We define the Kostant section in $\g^*$ using an identification $\g\simeq \g^*$ as discussed in Section \ref{s:dual}. That is we fix an equivariant isomorphism $\psi$, and define
$$
\K(X)=\psi(\K(\psi\inv(X))\quad (X\in \g^*).
$$
Since $\psi$ is unique on each simple factor up to a non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.

@@

\begin{lemma}[\phantom{}{\cite[Lemma 3.3.4]{adams_kaletha}}]
\label{lem:Kost_and_AC}
Let $\mathcal{O} \subset i\g(\R)^\ast$ be a regular semisimple orbit and  let~$X \in \g^\ast$ be a regular nilpotent element. Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$. 
\end{lemma}

@@

The two statements above, combined with Lemma \ref{lem:WF_and_AC}, give the following result,
which is a special case of the main result of \cite{matumoto} (Theorem A):

@@

If~$H$ is an element of~$\g$, write $\O_H$ for the $G(\R)$-orbit of $H$.

@@

\begin{proof}[Proof of the  Proposition]
For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.

@@

This proves the first assertion in the Proposition; the second assertion follows from the first and Lemma~\ref{lem:Kost_and_AC}.\end{proof}

@@

\subsection{$\AV$ and $\WF$: the Kostant--Sekiguchi correspondence } \label{sec:Sekiguchi}

@@

It is well known that there is a natural bijection between nilpotent $G(\R)$-orbits on $\g(\R)$ and nilpotent $K$ orbits on $\s$. 
This is the Kostant--Sekiguchi
correspondence~\cite{sekiguchi}, which we write as $\O \mapsto \KS(\O)$. It is a deep theorem of
Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront
set and the associated variety are related by this
correspondence. (As a historical aside, the Kostant--Sekiguchi
correspondence was discovered on the basis that the correspondence
$\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary
terms.)

@@

We need the corresponding result in $\g^*$. As discussed in Section \ref{s:dual} this uses a choice of an isomorphism $\psi\colon \g\to \g^*$, but the result is independent of this choice.
That is for $X\in \O_p\subset \g^*$ we have
$$
\KS(K\cdot X)=\psi(\KS(K\cdot \psi\inv(X)),
$$
independent of the choice of $\psi$.

@@

\section{Appendix: the case of $SL(2,\R)$}
